On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-04-20 engineering.tex
overall review (minor changes)
spellcheck
add features considered of a functional block

	a communication occurred and results in

@@

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent $a$ 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture can be expressed as a
relation between input and output belief, similarly to the quality of a channel
but inverting the flow (input$\rightarrow$output instead of
output$\rightarrow$input).  One may, of course, argue that since there is a
transformation process in the functional block the quality of that
transformation process is what the theory should consider. This can
be argued not just for functional blocks (Behaviors) but also for Channels
(Assertions). As we detail afterwards, the relations considered so
far revolves around the concept of integrity or availability, while the reminder of this section 
will be focused on a broader analysis of security properties and requirements
which will also consider other security properties such as availability and
confidentiality.  In order to define the quality of the internals of a functional block or channel, we first
need to relate the concept of Facts to engineering requirements.

@@

While availability and integrity are architectural property, meaning that they
can be expressed over the behavior of a port or a channel (as constituent of
the physical or functional architecture), confidentiality is not.
Confidentiality states that an information shall not be understood and not that
the information shall not be retrieved. So, if a port leaks an entire message,
there is no confidentiality issue in general, unless that message was not
encrypted at all, in which case the confidentiality leakage is straightforward. 
On the other hand, if the
information is not provided or altered there is an availability or integrity
issue. A similar argument can be proposed for integrity sub-properties such as
authenticity or non-repudiation. No wonder why it is often stated that
availability and integrity are the first properties to be considered in CPS
while confidentiality takes the first place when dealing with security
protocols. In fact, integrity is often assumed by pattern-matching (e.g. in
AVANTSSAR \autocite{avantssar}) and availability is hardly ever considered in
protocol verification. The question is, can we express properties such as
confidentiality, authentication, or non-repudiation as architectural properties
in $\abftheory$-theory? Confidentiality is based on the concept 
of secrecy so we shall first start from describing what secrecy is and how it
can be used to guarantee confidentiality in a system.

>>>>

	a communication occurred and resulted in

@@

\begin{definition}{\bf Functional Block and Architecture --}\label{def:funblock}
	A functional block of an agent $a$ 
	takes a region of input-Beliefs and outputs a region of output-Beliefs. 
	A functional architecture is an interconnected system of functional blocks.
\end{definition}
The quality of a functional block or architecture can be expressed as a
relation between input and output belief, similarly to the quality of a channel
but inverting the flow (input$\rightarrow$output instead of
output$\rightarrow$input). In other words, we consider two properties:
how inputs are interpreted, and how outputs are produced.
One may, of course, argue that since there is a
transformation process in the functional block the quality of that
transformation process is what the theory should consider. This can
be argued not just for functional blocks (Behaviors) but also for Channels
(Assertions). As we detail afterwards, the relations considered so
far revolves around the concept of integrity or availability, while the reminder of this section 
will be focused on a broader analysis of security properties and requirements
which will also consider other security properties such as availability and
confidentiality.  In order to define the quality of the internals of a functional block or channel, we first
need to relate the concept of Facts to engineering requirements.

@@

While availability and integrity are architectural property, meaning that they
can be expressed over the behavior of a port or a channel (as constituent of
the physical or functional architecture), confidentiality is not.
Confidentiality states that an information shall not be understood and not that
the information shall not be retrieved. So, if a port leaks an entire message,
there is no confidentiality issue in general, unless that message was not
encrypted at all, in which case the confidentiality leakage is straightforward. 
On the other hand, if the
information is not provided or altered there is an availability or integrity
issue. A similar argument can be proposed for integrity sub-properties such as
authenticity or non-repudiation. No wonder why it is often stated that
availability and integrity are the first properties to be considered in CPS
while confidentiality takes the first place when dealing with security
protocols. In fact, integrity is often assumed by pattern-matching (e.g. in
AVANTSSAR \autocite{Armando2012avantssar}) and availability is hardly ever considered in
protocol verification. The question is, can we express properties such as
confidentiality, authentication, or non-repudiation as architectural properties
in $\abftheory$-theory? Confidentiality is based on the concept 
of secrecy so we shall first start from describing what secrecy is and how it
can be used to guarantee confidentiality in a system.
